Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-04-14 talk/icooolps2011/paper.tex
go back to old definition and say something about side effects. kill section.

XXX not too happy with the definition

This hint can be used to mark functions as \emph{trace-elidable}. A function is
termed trace-elidable if, during the execution of the program, the results of
subsequent calls to the function with identical arguments may be be replaced
with the result of the first call without changing the program's behaviour.
From this
definition follows that a call to an trace-elidable function with constant arguments
in a trace can be replaced with the result of the call.\footnote{This property
is less strict than that of a "pure" function, because it is only about actual
calls during execution. All pure functions are trace-elidable though.}

@@

\subsubsection{Observably trace-elidable Functions}

\cfbolz{XXX do we kill this section?}

Why can't we simply write an analysis to find out that the \texttt{x} fields of the
\texttt{A} instances is immutable and deduce that \texttt{compute} is a trace-elidable function,
since it only reads the \texttt{x} field and does not have side effects? This might
be possible in this particular case, but in practice the functions that are
annotated with the \texttt{elidable} decorator are usually more complex.
The easiest example for this is that of a function that uses memoization to
cache its results. If this function is analyzed, it looks like the function has
side effects, because it changes the memoizing dictionary. However, because this side
effect is not externally visible, the function is still trace-elidable. This is
a property that is not easily detectable by analysis.

>>>>

This hint can be used to mark functions as \emph{trace-elidable}. A function is
termed trace-elidable if, during the execution of the program,
successive calls to the function with identical arguments always return the
same result. In addition the function needs to have no side effects or
idempotent side effects\footnote{This property
is less strict than that of a pure function, because it is only about actual
calls during execution. All pure functions are trace-elidable though.}.
From this definition follows that a call to an trace-elidable function with
constant arguments in a trace can be replaced with the result of the call.

@@
